Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-06-01 paper.tex
1 June 2015 9:30
Update paper.tex

According to (\cite{van2006landslide}) the magnitude of a possible
slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event. Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for applications where the complexity of the data detect complex nonlinear relationships, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.

>>>>

According to (\cite{van2006landslide}) the magnitude of a possible
slide is difficult to foresee as it depends on the magnitude of the triggering event and the environmental conditions (e.g., height of water table) at the moment of the event. Because of these complex relationships between the dependent variable and causal factors, and since that neural networks are particularly useful for detect complex non-linear relationships in large datasets, that is why this kind of model was chosen, despite the disadvantages such as greater computational burden and proneness to overfitting.
